### 2019-08-22 maciek.tex
Omega(kl)

  At this point we already know the sequence $\langle x^{(i)}\rangle$ of DET.
  For the requests of $I_2'$ to be free for OPT, it suffices to choose $v^D_0$ that is neither $d^{(1)}$ nor $d^{(2)}$,
  and to guarantee that $d^{(1)}$, $d^{(2)}$ does not appear in the sequence $\langle x^{(i)}\rangle$, i.e., to finish the input sequence before that.
  Furthermore, we would like to guarantee the length of $\langle x^{(i)}\rangle$ to remain $\Omega(k\cdot \ell)$.

>>>>

  At this point we already know the sequence $\langle x^{(i)}\rangle$ of DET.
  For the requests of $I_2'$ to be free for OPT, it suffices to choose $v^D_0$ that is neither $d^{(1)}$ nor $d^{(2)}$ (which is always possible for $k>3$),
  and to guarantee that $d^{(1)}$, $d^{(2)}$ does not appear in the sequence $\langle x^{(i)}\rangle$, i.e., to finish the input sequence before that.
  Furthermore, we would like to guarantee the length of $\langle x^{(i)}\rangle$ to remain $\Omega(k\cdot \ell)$.
